---
title: "Lab 03 - Nobel laureates"
author: "Insert your name here"
date: "Insert date here"
output: github_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(dplyr)
```

```{r load-data, message=FALSE}
nobel <- read_csv("data/nobel.csv")
```

## Exercises

Here is a link to the [lab instructions](https://datascience4psych.github.io/DataScience4Psych/lab03.html).

### Exercise 1

```{r}
nrow(nobel)

ncol(nobel)

```

The dataset contains `r nrow(nobel)` observations and `r ncol(nobel)` variables. Each row represents a single Nobel Prize laureate.

### Exercise 2

```{r}
nobel_living <- nobel %>%
  filter(
    is.na(died_date),
    !is.na(country),
    gender != "org"
  )

```
The nobel_living dataset contains `r nrow(nobel_living)` observations.

### Exercise 3

Remove this text, and add your answer for Exercise 1 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 4

...

### Exercise 5

...

### Exercise 6

...
